\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-19 evaluation.tex
updates in evaluation

For the MigratingTable case study, the first 7 bugs in Table~\ref{tab:testing} were discovered using a \psharp test harness based on nondeterministically generated, but controlled by \psharp, input history. For each of these found bugs, we manually reviewed one of the bug traces to confirm if it reflected the expected bug. The remaining 4 bugs (denoted with $\diamond$) are known bugs that we were unable to find with the fully-randomized test harness in the 100,000 iterations. We believe this is due to unlucky random choices of inputs and schedules by the \psharp testing engine. We wrote a custom \psharp test harness for each of these bugs, which allowed \psharp to quickly reproduce them. Note that using a custom test harness does not represent a testing method one could use to find unknown bugs in software. However, in this case the objective was to simply reproduce these known bugs.

>>>>

For the MigratingTable case study, the first 7 bugs in Table~\ref{tab:testing} were discovered using a \psharp test harness based on nondeterministically generated, but controlled by \psharp, input history. For each of these found bugs, we manually reviewed one of the bug traces to confirm if it reflected the expected bug. The remaining 4 bugs (denoted with $\diamond$) were not caught with our default test harness in the 100,000 iterations. We believe this is due to unlucky random choices of inputs and schedules by the \psharp testing engine. We wrote a custom \psharp test harness for each of these bugs, which allowed \psharp to quickly reproduce them. The design of these custom harnesses was influenced by the knowledge of these bugs; our objective here was to simply see if \psharp can reproduce these known bugs.
